Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
admissibility in g0 example, add pic, g0 saturation

\begin{defn}
\textbf{Saturations} of the canonical divisor, as defined in 7.
2 of VZB \cite{vzb:stacky}.
\end{defn}

@@

\ssec{Saturation}
\label{ssec:g_0_saturation} \todo{Define saturation}
Here we compute saturation numbers. That is, given a list of
ramification orders, with $g = 0,\delta = 0$ understood, we have
the following saturations of the canonical divisor, as defined in 7.
2 of Voight and Zureick-Brown \cite{vzb:stacky}. Exceptional cases are listed first
and generic cases follow.

\todo{prove}

@@

\begin{example}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $\halfcan \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

@@

By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
and Zureick-Brown \cite{vzb:stacky}),
\[
	H^0 (\sx', \lfloor 21 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan \rfloor)
\]

@@

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan)$ are generated by lower degrees for $d = 6$
and $7 < d \leq 24$. Note that we can again use Max Noether's theorem
(taking saturation into account) to see that

\begin{align*}
	&H^0 (\sx', \lfloor 3 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 3) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
	&H^0 (\sx', \lfloor 7 \halfcan \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 7) \halfcan \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
	\text{ (mod } 7)
\end{align*}

@@

\noindent
generated by quadratics under grevlex with $x_{i, j} \prec x_{k, l}$
if $i > j$ or $i = j$ and $j < l$. These quadratics must also 
determine minimal generators for $I$ by Lemma
~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to degree
$e = 7$ with relations up to degree $2e = 14$, as desired.

Now we check admissibility.

\end{example}

\begin{proof}
For these cases, we can always find a presentation satisfying (Ad-i).
Furthermore, we can verify that these base cases satisfy the
remaining conditions using computations of Riemann-Roch and pole
orders similar to those in the given example.

@@

All that remains to be shown is that these cases satisfy
(Ad-ii) and that $in_\prec(I')$ is minimally generated by
products of two monomials. The procedure for verifying these
are similar to those for the given example. Below, we
give a table for the explicit generators and initial ideals.
\todo{make table}
\end{proof}

>>>>

\begin{defn}
\label{defn:sat}
\textbf{Saturations} of the canonical divisor, as defined in 7.
2 of VZB \cite{vzb:stacky}.
\end{defn}

@@

\ssec{Saturation}
\label{ssec:g_0_saturation}
First, we present the saturations $s$ of the canonical divisor for
all cases where $g = 0, \delta = 0$ as defined in Definition
~\ref{defn:sat}. The saturation can be computed via the application
of Riemann-Roch on degrees up to $s$. Exceptional cases are listed
first and generic cases follow.

@@

\begin{example}
\label{ex:base-377}
Here we demonstrate, in detail, that case (b) ($\sigma_2 =
(0; 3, 7, 7; 0), J_2 = \{3, 4\}$) satisfies the conditions.
We have that $\halfcan' \sim -(\infty) + \frac{1}{3} P_1 + \frac{3}{7}
P_2 + \frac{3}{7} P_3$ for some points $P_i \neq \infty$.
We exhibit a (minimal) presentation for $R'$.

@@

By Max Noether's theorem over $\BP^1$ (see Lemma 3.1.1 of Voight
and Zureick-Brown \cite{vzb:stacky}),
\[
	H^0 (\sx', \lfloor 21 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 21) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor)
\]

@@

To show that these generate all of $R'$, we need to show that all
$H^0 (\sx', d \halfcan')$ are generated by lower degrees for $d = 6$
and $7 < d \leq 24$. Note that we can again use Max Noether's theorem
(taking saturation into account) to see that

\begin{align*}
	&H^0 (\sx', \lfloor 3 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 3) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor) \text{ if } d \geq 12 \text{ and } 3 \nmid d \\
	&H^0 (\sx', \lfloor 7 \halfcan' \rfloor) \otimes H^0 (\sx', \lfloor
	(d - 7) \halfcan' \rfloor) \twoheadrightarrow H^0 (\sx', \lfloor
	d \halfcan' \rfloor) \text{ if } d \geq 6, d \not\equiv 0, 5
	\text{ (mod } 7)
\end{align*}

@@

\noindent
generated by quadratics under grevlex with $x_{i, j} \prec x_{k, l}$
if $i > j$ or $i = j$ and $j < l$. These quadratics must also 
determine minimal generators for $I$ by Lemma
~\ref{lem:minimal_quadratic}. Thus, $R'$ is generated up to degree
$e = 7$ with relations up to degree $2e = 14$, as desired.
We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
since $e_i = 9 > e$ for all $i \in J$.

\todo{show only relations}

Admissibility is the remaining condition to check. WLOG, we can
let $x_{7, 1}$ correspond to the generator with maximal pole order
at $P_2$ and $x_{7, 2}$ correspond to the generator with maximal
pole order at $P_3$. Use the presentation given above with $y
_{2, e_2'} := x_{7, 1}$ and $y_{3, e_3'} :=  x_{7, 2}$. We see that
it immediately satisfies (Ad-i) of Definition ~\ref{defn:admissible}.
It also satisfies (Ad-ii) because $y_{i, e_i'}$ is the only generator
lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$ in the
$(\deg z, -ord_{P_i}(z))$ lattice and the other generators
must lie below the line as seen below:

\begin{center}
\includegraphics{pics/spin-377-pic-pics.pdf}
\end{center}

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J_2 = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $S_{\sigma_2, J_2}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 * 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and $\sigma_2, J_2$ is
admissible.
\end{example}

\begin{proof}
For the remaining cases, we can use a similar method to the one
used in Example ~\ref{ex:base-377} to find a presentation the
desired conditions.

@@

All that remains to be shown is that these cases satisfy
(Ad-i) and (Ad-ii) and that $in_\prec(I')$ is minimally generated by
products of two monomials. The procedure for verifying these
are similar to those for the given example. Below, we
give a table for the explicit generators and initial ideals.
\todo{make table, move this before (Ad-iii)?}
\end{proof}
